Efficient and Effective Metric Space Indexing for Complete Record Linkage Al: Exploring approaches to probabilistic record linkage using similarity searching (metric space indexing?)

### 2017-11-17 paper.tex
2017-11-17

% peter: below fast -> I would remove fast, as it might be slow for
% certain parameter settings
The LSH-minhash approach is a fast but inexact method of performing similarity search. It has three tuning parameters:
\emph{shingle size}, $l_{ss}$, the \emph{band size}, $l_{bs}$, and the
\emph{number of bands}, $l_{nb}$. These are explained in the following algorithm description which follows a standard LSH approach~\cite{??}.
Firstly all the fields of the record are turned into strings and 
concatenated. Next the strings are \emph{shingled} into a set of
n-grams (sub-strings of length $n$) according to the $l_{ss}$
parameter (i.e.\ $n = l_{ss}$). Next a set of randomly, 
deterministically generated hash functions are applied to each of the
sets of n-grams and the smallest (the minhash) of each application is
added to a signature. The number of hashes used and thus the size of
the signature is set to $l_{nb} \times l_{bs}$.
Lastly the signature is divided into $l_{nb}$ segments and the elements from the band are hashed again to create a number of keys.
The original record is added to a hashmap associated with each of the keys. It can be shown that the similarities between signatures generated in the second step have very close Jaccard similarity to the original string~\cite{lsh ref} and that if an arbitrary record is run through
% Peter: run through.. -> reword: is converted into such a LSH
% signature then..  records with the same key(s) are...
% Peter: close to.. -> is a bit vague
this process the records found in the map are close to the record being searched with good precision and recall. We will further explore these properties in this paper.
% peter: we will evaluate the performance of LSH based blocking with
% regard to the three parameters $l_{ss}$, $l_{bs}$ and $l_{nb}$ in
% Sect.~\ref{sec-exp}.
% peter: below - we want to do record linkage (slightly different
% from nn search) - better to describe RL below not NN search! 
To perform a {\textit{nearest-neighbour}} lookup, the query value is hashed using the procedure described above and the union of set of of values found for all hashes in the hashmap are returned. If desired, these may then be filtered by performing distance calculations on the results.

>>>>

% peter: below fast -> I would remove fast, as it might be slow for
% certain parameter settings
The LSH-minhash approach is a fast but inexact method of performing similarity search. It has three tuning parameters:
\emph{shingle size}, $l_{ss}$, the \emph{band size}, $l_{bs}$, and the
\emph{number of bands}, $l_{nb}$. These are explained in the following algorithm description which follows a standard LSH approach [CITATION].
Firstly all the fields of the record are turned into strings and 
concatenated. Next the strings are \emph{shingled} into a set of
n-grams (sub-strings of length $n$) according to the $l_{ss}$
parameter (i.e.\ $n = l_{ss}$). Next a set of randomly, 
deterministically generated hash functions are applied to each of the
sets of n-grams and the smallest (the minhash) of each application is
added to a signature. The number of hashes used and thus the size of
the signature is set to $l_{nb} \times l_{bs}$.
Lastly the signature is divided into $l_{nb}$ segments and the elements from the band are hashed again to create a number of keys.
The original record is added to a hashmap associated with each of the keys. It can be shown that the similarities between signatures generated in the second step have very close Jaccard similarity to the original string [LSH CITATION] and that if an arbitrary record is run through
% Peter: run through.. -> reword: is converted into such a LSH
% signature then..  records with the same key(s) are...
% Peter: close to.. -> is a bit vague
this process the records found in the map are close to the record being searched with good precision and recall. We will further explore these properties in this paper.
% peter: we will evaluate the performance of LSH based blocking with
% regard to the three parameters $l_{ss}$, $l_{bs}$ and $l_{nb}$ in
% Sect.~\ref{sec-exp}.
% peter: below - we want to do record linkage (slightly different
% from nn search) - better to describe RL below not NN search! 
To perform a {\textit{nearest-neighbour}} lookup, the query value is hashed using the procedure described above and the union of set of of values found for all hashes in the hashmap are returned. If desired, these may then be filtered by performing distance calculations on the results.
